\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2\\
Mitchell Weingust & 2\\
Parisha Nizam & 2\\
Promish Kandel & 2\\
Jasmine Sun-Hu & 2\\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 4\\
Mitchell Weingust & 4\\
Parisha Nizam & 4\\
Promish Kandel & 3\\
Jasmine Sun-Hu & 4\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Mitchell Weingust & 2\\
Parisha Nizam & 1\\
Promish Kandel & 0\\
Jasmine Sun-Hu & 2\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 2\\
Mitchell Weingust & 2\\
Parisha Nizam & 2\\
Promish Kandel & 2\\
Jasmine Sun-Hu & 2\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 214 & 100\% \\
Mitchell Weingust & 63 & 29.44\% \\
Parisha Nizam & 87 & 40.66\% \\
Promish Kandel & 13 & 6.07\% \\
Jasmine Sun-Hu & 51 & 23.83\% \\
\bottomrule
\end{tabular}
\end{table}

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Mitchell Weingust & 48 & 67 \\
Parisha Nizam & 33 & 52 \\
Promish Kandel & 0 & 30 \\
Jasmine Sun-Hu & 32 & 52 \\
\bottomrule
\end{tabular}
\end{table}

\section{Productivity}
We have the following metrics that we tracked to ensure optimal productivity from each team member

\begin{itemize}
    \item Attendance: 95\% of all team meetings
    \item Commits: At least 3 meaningful commits per Deliverable (Meaningful means: 10-15 lines of code (minimum) changed per commit)
    \item Confirm review of all documents prior to submission
    \item Confirm review of all rubric criteria prior to submission
\end{itemize}

  As of March 26th 2025, all Productivity criteria have been met. 
  \begin{itemize}
    \item Attendance: 95\% of all team meetings
        \subitem{All team members have been to 100\% of team meetings.
    \item Commits: At least 3 meaningful commits per Deliverable (Meaningful means: 10-15 lines of code (minimum) changed per commit).}
        \subitem{Within this period of interest, we have had the V\&V Report and Revision 0. A minimum of 3 commits were
        achieved for each deliverable. Additionally, minimum 3 commits were achieved by each group member per deliverable.}
        \subitem{Each team member's total number of commits is well above 6 (3 V\&V Report + 3 revision 1), with an average of 53 commits across team members.}
    \item Confirm review of all documents prior to submission
        \subitem{All team members met in person to confirm review of all documents and deliverables prior to submission}
    \item Confirm review of all rubric criteria prior to submission
        \subitem{All team members met in person to confirm review of all documents and deliverables prior to submission while comparing it to the rubric criteria}
  \end{itemize}

\end{document}