\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

\hspace{2em}In the proof of concept demonstration, the team will showcase an interactive interface that displays the front 
camera of the device to detect and respond to specific visual inputs. When a user places their face in front 
facing view of the camera, the application will recognize when the user uses hand gestures in view of the camera, 
or when multiple faces are detected in the view. The interface will provide feedback by displaying what action it 
detects below the displayed camera feed within 3 seconds of the action itself. 

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 7\\
Mitchell Weingust & 7\\
Jasmine Sun-Hu & 7\\
Parisha Nizam & 7\\
Promish Kandel & 7\\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 6\\
Mitchell Weingust & 6\\
Jasmine Sun-Hu & 6\\
Parisha Nizam & 5\\
Promish Kandel & 5\\
\bottomrule
\end{tabular}
\end{table}

\hspace{2em}Promish and Parisha each missed one meeting when they were sick. All team members attended supervisor and stakeholder meetings when the circumstances allowed it.
If a team member missed a meeting, they caught themselves up by reviewing meeting notes and talking with other teammates.

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 12\\
Mitchell Weingust & 11\\
Jasmine Sun-Hu & 10\\
Parisha Nizam & 9\\
Promish Kandel & 6\\
\bottomrule
\end{tabular}
\end{table}

\hspace{2em}All members of the team missed the lecture on September 10th, as it was the Mechatronics
specific lecture.
Mitchell was the delegate for the group on the October 23rd lecture, as the rest of the group had
a midterm directly following.\\

\section{TA Document Discussion Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 3\\
Mitchell Weingust & 3\\
Jasmine Sun-Hu & 3\\
Parisha Nizam & 3\\
Promish Kandel & 3\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 187 & 100\% \\
Mitchell Weingust & 48 & 25.66\% \\
Jasmine Sun-Hu & 62 & 33.15\%\\
Parisha Nizam & 32 & 17.11\% \\
Promish Kandel & 45 & 24.06\% \\
\bottomrule
\end{tabular}
\end{table}

The total number of commits involve all branches merged to main.

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Mitchell Weingust & 143 & 40 \\
Jasmine Sun-Hu & 11 & 43 \\
Parisha Nizam & 3 & 44 \\
Promish Kandel & 4 & 37 \\
\bottomrule
\end{tabular}
\end{table}

For the authored issues, Mitchell was elected to create the issues for the team for organizational purposes. Assigned issues are distributed evenly, disparities are due to 
cases where when dividing the workload one team member is assigned a few larger sections, and another is assigned multiple smaller sections.

\section{CICD}
\begin{itemize}
	\item GitHub Actions will be used to create and manage continuous integration workflow scripts.
	\begin{itemize}
    \item Running a code linting tool and automatically enforcing style guides
    \item Restricting the ability to merge pull requests that do not meet our coding standards
    \item Perform PR check: PR template is filled correctly such as correct labels and issues are linked properly to PR. 
    \item Ensure that the code builds successfully on each push
  \end{itemize}
	\item If all tests pass, and at least one team members review the pull request, the branch can be approved and merged 
    into the main branch.
	\item The lead developer will ensure all necessary code is covered by automated tests.
	\item A rollback strategy will be included in the CD pipeline in case the project needs 
  to be reverted to a previously stable state.
\end{itemize}

The CI/CD will be used further to run more unit tests for PRs's once developed from MIS in the VnvPlan 
as well as automatically adding applicable labels to PRs based on the code change. 

\section{Productivity}
We have the following metrics that we will track to ensure optimal productivity from each team member

\begin{itemize}
    \item Attendance: 95\% of all team meetings
    \item Commits: At least 3 meaningful commits per Deliverable (Meaningful means: 10-15 lines of code (minimum) changed per commit)
    \item Confirm review of all documents prior to submission
    \item Confirm review of all rubric criteria prior to submission
  \end{itemize}

  As of November 6th 2024, all Productivity criteria has been met. 
  \begin{itemize}
    \item Attendance: 95\% of all team meetings
        \subitem{2 team members have been to 100\% team meetings, with 2 members missing 1 meeting due to health reasons. 
    \item Commits: At least 3 meaningful commits per Deliverable (Meaningful means: 10-15 lines of code (minimum) changed per commit).}
        \subitem{We have had 5 deliverables so far, Problem Statement, Development Plan, SRS, Hazard Analysis and VnV. A minimum of 3 commits was 
        required meaning a total of 15.}
        \subitem{Each team members total number of commits is well above 15, with an average of 47 commits across team members.}
    \item Confirm review of all documents prior to submission
        \subitem{All team members meet on a review call to go through document prior to submission}
    \item Confirm review of all rubric criteria prior to submission
        \subitem{All team members meet on a review call to go through document prior to submission while comparing it to the rubric criteria}
  \end{itemize}



\end{document}