\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the POC demo and the Rev
0 demo.

\section{Demo Plans}

\hspace{2em} In the Revision 0 demonstration, the team will demonstrate the full implementation of the system, showcasing
one full mock interaction. The demonstration will feature two laptops, with a live connection to an Amazon Web Services (AWS)
database. One laptop will have the parent view, with another laptop the clinician view.

The demonstration will consist of a client account completing 1 full assessment. The results, including the media recording and processing, will be saved
to the AWS server, where we will demonstrate the clinician view, consisting of reviewing their list of clients, their clients' past assessments,
and reviewing each question in an assessment. Within each question, we will demonstrate how a clinician can view if bias was detected, flagging a question
with bias detected, removing bias, and reviewing the answer to a question.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 5\\
Mitchell Weingust & 5\\
Parisha Nizam & 5\\
Jasmine Sun-Hu & 4\\
Promish Kandel & 5\\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 4\\
Mitchell Weingust & 4\\
Parisha Nizam & 3\\
Jasmine Sun-Hu & 4\\
Promish Kandel & 3\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 3\\
Mitchell Weingust & 3\\
Parisha Nizam & 1\\
Jasmine Sun-Hu & 1\\
Promish Kandel & 0\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Mitchell Weingust & 1\\
Parisha Nizam & 1\\
Jasmine Sun-Hu & 1\\
Promish Kandel & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 141 & 100\% \\
Mitchell Weingust & 38 & 27\% \\
Parisha Nizam & 12 & 8\% \\
Jasmine Sun-Hu & 25 & 18\% \\
Promish Kandel & 66 & 47\% \\
\bottomrule
\end{tabular}
\end{table}

Parisha Nizam: My Git commit count is lower because I previously made larger commits instead of smaller, incremental ones. I'm now making a more conscious effort to push changes more frequently and follow best practices for version control.

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Mitchell Weingust & 135 & 58 \\
Parisha Nizam & 1 & 39 \\
Jasmine Sun-Hu & 3 & 52 \\
Promish Kandel & 2 & 33 \\
\bottomrule
\end{tabular}
\end{table}


\section{CICD}

\begin{itemize}
	\item GitHub Actions will be used to create and manage continuous integration workflow scripts.
	\begin{itemize}
    \item Running a code linting tool and automatically enforcing style guides
    \item Restricting the ability to merge pull requests that do not meet our coding standards
    \item Perform PR check: PR template is filled correctly such as correct labels and issues are linked properly to PR. 
    \item Ensure that the code builds successfully on each push
  \end{itemize}
	\item If all tests pass, and at least one team members review the pull request, the branch can be approved and merged 
    into the main branch.
	\item The lead developer will ensure all necessary code is covered by automated tests.
	\item A rollback strategy will be included in the CD pipeline in case the project needs 
  to be reverted to a previously stable state.
\end{itemize}

The CI/CD will be used further to run more unit tests for PRs's once developed from MIS in the VnvPlan 
as well as automatically adding applicable labels to PRs based on the code change. 

\section{Productivity}
We have the following metrics that we will track to ensure optimal productivity from each team member

\begin{itemize}
    \item Attendance: 95\% of all team meetings
    \item Commits: At least 3 meaningful commits per Deliverable (Meaningful means: 10-15 lines of code (minimum) changed per commit)
    \item Confirm review of all documents prior to submission
    \item Confirm review of all rubric criteria prior to submission
\end{itemize}

  As of January 29th 2025, all Productivity criteria have been met. 
  \begin{itemize}
    \item Attendance: 95\% of all team meetings
        \subitem{3 team members have been to 100\% of team meetings, with 1 members missing 1 meeting due to health reasons. 
    \item Commits: At least 3 meaningful commits per Deliverable (Meaningful means: 10-15 lines of code (minimum) changed per commit).}
        \subitem{Within this period of interest, we have had the Design Document and Revision 0. A minimum of 3 commits were
        achieved for each deliverable. Additionally, minimum 3 commits were achieved by each group member per deliverable.}
        \subitem{Each team member's total number of commits is well above 6 (3 design document + 3 revision 0), with an average of 35 commits across team members.}
    \item Confirm review of all documents prior to submission
        \subitem{All team members met in person to confirm review of all documents and deliverables prior to submission}
    \item Confirm review of all rubric criteria prior to submission
        \subitem{All team members met in person to confirm review of all documents and deliverables prior to submission while comparing it to the rubric criteria}
  \end{itemize}

\end{document}